
\section*{References}
\begin{sloppypar}

  \begin{enumerate}[label={[\arabic*]}]
  
    \item N. Naik, "Performance Evaluation of Distributed Systems in Multiple Clouds using Docker Swarm," 2021 \textit{IEEE International Systems Conference (SysCon)}, Vancouver, BC, Canada, 2021, pp. 1-6, doi: 10.1109/SysCon48628.2021.9447123

    \item “Create standard repositories,” \textit{Google Cloud}. [Online]. Available: https://cloud.google.com/artifact-registry/docs/repositories/create-repos.[Accessed: 29 June 2023].

    \item “Deploying to cloud run,” \textit{Google Cloud}. [Online]. Available: https://cloud.google.com/run/docs/deploying. [Accessed: 29 June 2023].

    \item “Add data to cloud firestore,” \textit{Firebase}. [Online]. Available: https://firebase.google.com/docs/firestore/manage-data/add-data. [Accessed: 29 June 2023].

    \item “Get data with cloud firestore,” \textit{Firebase}. [Online]. Available: https://firebase.google.com/docs/firestore/query-data/get-data. [Accessed: 29 June 2023].

    \item “Containerize an application,” \textit{Docker Documentation}, 28-Jun-2023. [Online]. Available: https://docs.docker.com/get-started/02\_our\_app/. [Accessed: 29 June 2023].


    \item	“Update the application,”\textit{ Docker Documentation}, 28-Jun-2023. [Online]. Available: https://docs.docker.com/get-started/03\_updating\_app/. [Accessed: 29 June 2023].


    \item “Push and pull images,”\textit{ Google Cloud}. [Online]. Available: https://cloud.google.com/artifact-registry/docs/docker/pushing-and-pulling. [Accessed: 29 June 2023].


    \item “Create a new react app,” \textit{Reactjs.org}. [Online]. Available: https://legacy.reactjs.org/docs/create-a-new-react-app.html. [Accessed: 29 June 2023].


    \item	S.Gandotra, “ReactJS router,” \textit{GeeksforGeeks}, 13-Dec-2019. [Online]. Available: https://www.geeksforgeeks.org/reactjs-router/. [Accessed: 29 June 2023].
    
    \item "LaTeX Listings package JSON formatting," \textit{TeX Stack Exchange}, Available: https://tex.stackexchange.com/questions/560830/latex-listings-package-json-formatting. [Accessed 29 June 2023].
    
    \item V. Venkatapathi, "B00936916_VikramVenkatapathi_A1_Report.pdf," \textit{Dalhousie University}, Jan. 2023. [Online]. Available: https://git.cs.dal.ca/vikramv/csci5408_w23_b00936916_vikram_venkatapathi/-/blob/main/Assignment_1/B00936916_VikramVenkatapathi_A1_Report.pdf. [Accessed 29 June 2023].
    
    \item Shanmuganathan, Vishakan. "OOAD-Project." \textit{GitHub}, 2021, https://github.com/svishakan/OOAD-Project. [Accessed 29 June 2023].

    \item AWS. "Amazon Lex V1",\textit{Amazon.com}[Online]. Available: https://docs.aws.amazon.com/lex/latest/dg/gs-bp-create-bot.html. [Accessed: 29 June 2023].

    \item “Swarm mode overview,” \textit{Docker Documentation}, 30-Jun-2023. [Online]. Available: https://docs.docker.com/engine/swarm/. [Accessed: 03 July 2023].

    \item R. Powell, “Docker Swarm vs Kubernetes: how to choose a container orchestration tool,” \textit{CircleCI}, 12-Oct-2021. [Online]. Available: https://circleci.com/blog/docker-swarm-vs-kubernetes/. [Accessed: 03 July 2023].

    \item “Production-Grade Container Orchestration,” \textit{Kubernetes}. [Online]. Available: https://kubernetes.io/. [Accessed: 03 July 2023].

    \item “Lightweight kubernetes,” \textit{K3s.io}. [Online]. Available: https://k3s.io/. [Accessed: 03 July 2023].

  \end{enumerate}

\end{sloppypar}
\newpage

