
\section*{References}
\begin{sloppypar}

  \begin{enumerate}[label={[\arabic*]}]
    \item P.  Vahidinia,  B.  Farahani  and F.  S.  Aliee,  "Mitigating Cold Start  Problem in  Serverless  Computing: A Reinforcement Learning  Approach,"   \textit{IEEE  Internet  of  Things  Journal},  doi: 10.1109/JIOT.2022.3165127.

    \item Eisenbarth, J.-P. (2010, July 3). "Inserting code in this LaTeX document with indentation". \textit{Stack Overflow}. Available: https://stackoverflow.com/questions/3175105/inserting-code-in-this-latex-document-with-indentation. [Accessed 07 June 2023].

    \item "Getting two pictures to appear on the same page," \textit{TeX Stack Exchange}, Available: https://tex.stackexchange.com/questions/134162/getting-two-pictures-to-appear-on-the-same-page. [Accessed 07 June 2023].

    \item "LaTeX Listings package JSON formatting," \textit{TeX Stack Exchange}, Available: https://tex.stackexchange.com/questions/560830/latex-listings-package-json-formatting. [Accessed 07 June 2023].

    \item V. Venkatapathi, "B00936916_VikramVenkatapathi_A1_Report.pdf," \textit{Dalhousie University}, Jan. 2023. [Online]. Available: https://git.cs.dal.ca/vikramv/csci5408_w23_b00936916_vikram_venkatapathi/-/blob/main/Assignment_1/B00936916_VikramVenkatapathi_A1_Report.pdf. [Accessed 07 June 2023].
    
    \item Shanmuganathan, Vishakan. "OOAD-Project." \textit{GitHub}, 2021, https://github.com/svishakan/OOAD-Project. [Accessed 07 June 2023].

    \item AWS SDK for Java Developer Guide., "Working with Amazon S3 Buckets".\textit{Amazon Web Services, Inc., 2022} [Online]. Available: https://docs.aws.amazon.com/sdk-for-java/latest/developer-guide/examples-s3-buckets.html. [Accessed 07 June 2023].

    \item AWS SDK for Java Developer Guide., "Working with Amazon S3 Objects". \textit{Amazon Web Services, Inc., 2022} [Online]. Available: https://docs.aws.amazon.com/sdk-for-java/latest/developer-guide/examples-s3-objects.html. [Accessed 07 June 2023].

    \item AWS Command Line Interface User Guide., "Configuration and Credential Files". \textit{Amazon Web Services, Inc., 2022} [Online]. Available: https://docs.aws.amazon.com/cli/latest/userguide/cli-configure-files.html. [Accessed 07 June 2023].


  \end{enumerate}

\end{sloppypar}
\newpage

